Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-23 articles/cycle/alps-cycle.tex
Add palaeo-temperature records table.

\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}

@@

\newcommand{\chem}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\unit}[1]{\ensuremath{\mathrm{#1}}}

@@

% ----------------------------------------------------------------------
% Figures
% ----------------------------------------------------------------------

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_erosion}}
      \caption{%
        \textbf{(a)} Modelled total erosion integrated in time over the entire
        simulation (120--0\,ka) is highest in the deep valleys and cirques of
        the western Alps.
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model (black curve),
        and modelled erosion rate integrated in space over the entire
        ice-covered area. The local erosion rate, $\dot{e}$, is computed from
        the sliding velocity, $\vec{v}_{\mathrm{b}}$, through
        $\dot{e} = K_g \cdot |\vec{v}_{\mathrm{b}}|^{l}$, with
        $l = 2.02$ and $K_g = 2.7 \cdot 10^{-7}\,m^{1-l}\,a^{l-1}$
        \citep{Herman.etal.2015}.}
      \label{fig:erosion}
    \end{figure}

% ----------------------------------------------------------------------
% Supplementary tables
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
% Supplementary figures
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
% ----------------------------------------------------------------------

>>>>

\usepackage{amsmath}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}

@@

% Common units
\newcommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\newcommand{\chem}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\unit}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\degree}[0]{\ensuremath{^{\circ}}}
\newcommand{\degC}[0]{\unit{{\degree}C}}

@@

% ----------------------------------------------------------------------
% Figures
\clearpage
% ----------------------------------------------------------------------

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_erosion}}
      \caption{%
        \textbf{(a)} Modelled total erosion integrated in time over the entire
        simulation (120--0\,ka) is highest in the deep valleys and cirques of
        the western Alps.
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model (black curve),
        and modelled erosion rate integrated in space over the entire
        ice-covered area. The local erosion rate, $\dot{e}$, is computed from
        the sliding velocity, $\vec{v}_{\mathrm{b}}$, through
        $\dot{e} = K_g \cdot |\vec{v}_{\mathrm{b}}|^{l}$, with
        $l = 2.02$ and $K_g = 2.7\e{-7}\,m^{1-l}\,a^{l-1}$
        \citep{Herman.etal.2015}.}
      \label{fig:erosion}
    \end{figure}

% ----------------------------------------------------------------------
% Supplementary tables
\clearpage
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
% ----------------------------------------------------------------------

    \begin{table*}
      \caption{%
        Palaeo-temperature proxy records and scaling factors yielding
        temperature offset time-series used to force the ice sheet model
        through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
        corresponds to the scaling factor adopted to yield Last Glacial Maximum
        ice limits in the vicinity of mapped end moraines
        (Fig.~\ref{fig:footprints}a), and $[{\Delta}T_{\textrm{TS}}]_{32}^{22}$
        refers to the resulting mean temperature anomaly during the period 32
        to~22\,\unit{ka} after scaling.}
      \label{tab:records}
      %\scalebox{.850}[.850]
      \centerline{\begin{tabular}{lccccccl}
        \toprule
        Record    & Latitude & Longitude & Elev. (m~a.s.l.)
                  & Proxy & $f$ & $[{\Delta}\text{TS}]_{32}^{22}$ (K)
                  & Reference\\
        \midrule
        GRIP      &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
                  &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
                  & 3238
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$7.6  % -16.4126 (before scaling)
                  & \citet{Dansgaard.etal.1993} \\
        EPICA     &  75{\degree}06$^{\prime}$\,S   % 75.1
                  & 123{\degree}21$^{\prime}$\,E   % 123.35
                  & 3233
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$9.5  % -9.2055
                  & \citet{Jouzel.etal.2007} \\
        MD01-2444 &  37{\degree}34$^{\prime}$\,N   % 37.561
                  &  10{\degree}04$^{\prime}$\,W   % -10.142
                  & $-$2637
                  & \chem{U^{K'}_{37}}
                  & 1.84 & $-$8.0  % -4.345625
                  & \citet{Martrat.etal.2007} \\
        \bottomrule
      \end{tabular}}
    \end{table*}

% ----------------------------------------------------------------------
% Supplementary figures
\clearpage
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
% ----------------------------------------------------------------------
